\documentclass[12pt]{article}

\usepackage{amssymb,amsmath,amsfonts,eurosym,geometry,multirow,ulem,graphicx,caption,color,setspace,sectsty,comment,footmisc,caption,natbib,pdflscape,subfig,array,hyperref,outlines,tikz,bbm,pgfplots}
\usepackage{enumitem}


\normalem

\newtheorem{theorem}{Theorem}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}{Proposition}
\newenvironment{proof}[1][Proof]{\noindent\textbf{#1.} }{\ \rule{0.5em}{0.5em}}

\newtheorem{hyp}{Hypothesis}
\newtheorem{subhyp}{Hypothesis}[hyp]
\renewcommand{\thesubhyp}{\thehyp\alph{subhyp}}

\newcommand{\red}[1]{{\color{red} #1}}
\newcommand{\blue}[1]{{\color{blue} #1}}

\newcolumntype{L}[1]{>{\raggedright\let\newline\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\arraybackslash\hspace{0pt}}m{#1}}

\geometry{left=1.0in,right=1.0in,top=1.0in,bottom=1.0in}

\newcommand{\argmax}[1]{\underset{#1}{\operatorname{arg}\operatorname{max}}\;}


\begin{document}

\begin{titlepage}

\setcounter{page}{1}

\title{\Large Does Franchise Expansion Affect Legislative Activity?:\\ Evidence from British India Legislative Debates, 1901-1940}
\author{Mitchell Bosley\thanks{PhD Candidate, Department of Political Science, University of Michigan. e-mail: mcbosley@umich.edu} and Htet Thiha Zaw\thanks{PhD Candidate, Department of Political Science, University of Michigan. e-mail: htzaw@umich.edu}}
\date{\today}
\maketitle
\begin{abstract}
\noindent Universal suffrage, the unconditional provision of voting rights for every adult citizen, is a key element of democracy. The transition from a more limited to less limited franchise, therefore, is purported to bring the many benefits of democracy, including widespread distribution of economic benefits to citizens. While existing research has identified such transformation by looking at policy outcomes, it lacks an explanation of how they were brought about in the legislature, a key actor in policy formation. We fill this gap with the first-ever text-as-data analysis of the British India legislature over four decades, two before franchise expansion and two after expansion. We find [positive/negative/no change] in topics on goods provision under debate after franchise expansion by constructing topic models for legislative debates. We see a [change/no change] in legislative behavior [both/either/neither] among elected members and appointed members, among Hindu and Muslim members, and among those representing constituencies with or without women's franchise. The findings enrich our existing knowledge on the linkages between democratization, legislative activity, and goods provision.\\
%\noindent\textbf{JEL Codes:} key1, key2, key3\\

\bigskip
\end{abstract}
\setcounter{page}{0}
\thispagestyle{empty}
\end{titlepage}
\pagebreak \newpage

\doublespacing

\end{document}
